---
title: "linear model from Web"
author: "Kimberly Aldana"
date: "Summer 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot


```{r}
basicNN <- ggplot(data, aes(y = SIMS, x = ARM)) +
geom_point() +
labs(title = "SIMS and ARM") +
theme(plot.title = element_text(hjust = 0.5))

basicNN
```


### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The numerical results for sims-arm is 0.6860073. This means there is a far relationship between the two variable strength.

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The residual standard error is 1.226, while the r- squared is 0.4786 . The comparison between the two, we always look at the adjusted r-squared numbers. As you put more data in your model, the adjusted r-squared will go up.


#### Predict at target point

```{r}
mydata<- data.frame(GRIP=88,ARM=104)
predict.lm(model.1,mydata,interval= "prediction" )
```

The value that it predicted was 1.57 in change but it can go to -0.863 to an upper positive 4.02 in change.

#### scatterplot with model fit
  
```{r}
basicNN <- ggplot(data, aes(y = SIMS, x = ARM)) +
geom_point() +
geom_smooth(method = "lm", se = FALSE) +
labs(title = "SIMS ~ ARM") +
theme(plot.title = element_text(hjust = 0.5))

basicNN

```  
  
  
## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
mygrip<- ggplot(data, aes(y = SIMS, x = GRIP)) +
geom_point() +
labs(title = "SIMS and GRIP") +
theme(plot.title = element_text(hjust = 0.5))

mygrip
```


### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

The numerical results for SIMS~GRIP is0.6398458. SIMS~ARM has a higher correlation than SIMS~GRIP.


### Inferential  (Build model.2)
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

The residual standard error is 1.295 and the r squared is 0.4094 SIMS~ARRM has a better residual error and a better r squared number than sims~grip.  

#### predict model.2 at target point

```{r}
predict.lm(model.2,mydata,interval= "prediction" )
```


#### now add the model fit to our plot for model.2
  
```{r}
mygrip <- ggplot(data, aes(y = SIMS, x = GRIP)) +
geom_point() +
geom_smooth(method = "lm", se = FALSE) +
labs(title = "SIMS ~ GRIP") +
theme(plot.title = element_text(hjust = 0.5))

mygrip

```


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
````
  
The correlation is larger  
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

